Arrows for Parallel Computations

### 2017-06-02 paper/content/mapSkeletons.tex
.

A |parMap| (Figs.~\ref{fig:parMapImg},~\ref{fig:parMap}) spawns every single computation in a new thread (at least for the instances of |ArrowParallel| we gave in this paper). This can be quite wasteful and a |farm| (Fig.~\ref{fig:farmImg},~\ref{fig:farm}) that equally distributes the workload over |numCores| workers (if numCores is greater than the actual processor count, the fastest processor(s) to finish will get more tasks) seems useful.
The definitions of helper functions |unshuffle|, |takeEach|, |shuffle| (Fig.~\ref{fig:edenshuffleetc}) originate from an Eden skeleton\footnote{Available on Hackage under \url{https://hackage.haskell.org/package/edenskel-2.1.0.0/docs/src/Control-Parallel-Eden-Map.html}.}.

>>>>

A |parMap| (Figs.~\ref{fig:parMapImg},~\ref{fig:parMap}) spawns every single computation in a new thread (at least for the instances of |ArrowParallel| we gave in this paper). This can be quite wasteful and a |farm| (Fig.~\ref{fig:farmImg},~\ref{fig:farm}) that equally distributes the workload over |numCores| workers (if numCores is greater than the actual processor count, the fastest processor(s) to finish will get more tasks) seems useful.
The definitions of the helper functions |unshuffle|, |takeEach|, |shuffle| (Fig.~\ref{fig:edenshuffleetc}) originate from an Eden skeleton\footnote{Available on Hackage under \url{https://hackage.haskell.org/package/edenskel-2.1.0.0/docs/src/Control-Parallel-Eden-Map.html}.}.
